\documentclass{domingosfelipe-resume}  

\name{Felipe Domingos}

\address{\href{https://www.linkedin.com/in/domingosfelipe/}{LinkedIn}}
\address{\href{mailto:contato@felipedomingos.com}{contato@felipedomingos.com}}
\address{\href{tel:+5551992643931}{+55 51 99264-3931}}

\begin{document}
    \resume{Summary}{Back-end Software Engineer with 17 years of experience specializing in Java (versions 8 to 21) and Spring Framework. Proven expertise in micro-services architecture, system integration, and performance optimization. Deep knowledge in SQL and NoSQL databases. Focused on delivering robust and scalable solutions, with a history of solving complex challenges and technical leadership in project implementation.}

    \begin{rSection}{Professional Experience}
    \begin{rExperienceSubsection}{CashGO}{Back-end Engineer}{2023}{Present}
        \item Migrated backend solutions from Java 17 to Java 21 using Spring 3.x, ensuring compatibility with recent versions and improved performance.
        \item Actively monitored for critical issues, facilitating agile incident resolution.
        \item Configured and managed repositories and CI/CD pipelines on GitHub, accelerating development cycles.
        \item Analyzed and optimized micro-services performance, resulting in more efficient and scalable applications.
        \item \textbf{Key projects:} Implemented back-end solution for managing real estate owners, integrating data from property systems across Brazil. Actively participated in the implementation of a document OCR solution using Artificial Intelligence for automated information extraction.
    \end{rExperienceSubsection}

    \begin{rExperienceSubsection}{CWI Software}{Back-end Developer}{2021}{2023}
        \item Worked in multidisciplinary teams developing solutions for \textbf{Sumicity} and \textbf{VIP Telecom}.
        \item Developed and maintained micro-services for sales and modem provisioning systems, ensuring scalability and reliability.
        \item Analyzed API integrations and optimized performance, improving inter-service communications.
        \item Configured repositories and CI/CD pipelines on GitLab, speeding up software delivery.
        \item \textbf{Main Project:} Led back-end implementation for modem provisioning solution, automating manual workflows and enabling remote configurations by customers.
    \end{rExperienceSubsection}

    \begin{rExperienceSubsection}{Resource IT Solutions}{Back-end Developer}{2020}{2021}
        \item Developed micro-services for contract and warranty management systems, ensuring scalability and ease of maintenance.
        \item Configured repositories and CI/CD pipelines on GitLab, enabling continuous integration and continuous delivery.
        \item \textbf{Main Project:} Implemented solutions using Spring WebFlux, significantly reducing processing time and increasing system reliability.
    \end{rExperienceSubsection}

    \begin{rExperienceSubsection}{DBserver}{Back-end Developer}{2020}{2020}
        \item Developed micro-services for credit availability analysis systems, ensuring performance and reliability.
        \item \textbf{Main Project:} Enhanced efficiency of legacy systems through refactoring and implementing new solutions, fully replacing outdated systems and resulting in faster and safer operations.
    \end{rExperienceSubsection}

    \begin{rExperienceSubsection}{SRM Asset}{Back-end Developer}{2018}{2020}
        \item Developed back-end solutions for Home Banking platforms in Brazil and Peru, ensuring high performance and application security.
        \item Configured repositories and CI/CD pipelines on GitLab, supporting continuous integration and frequent deliveries.
        \item \textbf{Main Project:} Led back-end implementation of a document management system, automating manual processes and improving platform security.
    \end{rExperienceSubsection}
    \end{rSection}

    \begin{rSection}{Education}
        \begin{rEducationSubsection}{Pontifícia Universidade Católica do Rio Grande do Sul – PUCRS}{2018}    
            \item Bachelor's Degree in Information Systems.
        \end{rEducationSubsection}
    \end{rSection}

    \begin{rSection}{Certificates}
        \begin{rSkillsSubsection}
            \item \href{https://www.linkedin.com/learning/certificates/3781e6e11a2fe389fcb48387012853f893c2bdbc3decd7c57790c2c850c316be?trk=share_certificate}{GitHub}
            \item \href{https://www.linkedin.com/learning/certificates/bd30b94ff1b980132e44f68668e4a1c56b9fddb10832c9c01d9d65ce7d2b9c62?trk=share_certificate}{Docker Foundations}
        \end{rSkillsSubsection}
    \end{rSection}

    \begin{rSection}{Skills}
        \item \textbf{Technologies:} Java 8+, Spring Framework, SQL, NoSQL, AWS, Messaging, JavaScript, React.
        \item Microservices Architecture, Design Patterns, Software Architecture, Algorithms and Data Structures.
        \item \textbf{DevOps and Tools:} GitHub, GitLab, CI/CD, Docker.
        \item Agile methodologies (Scrum, Kanban).
        \item Technical Leadership and Team Management.
    \end{rSection}

\end{document}
